Debugging by \textit{lastChange}

### 2010-10-13 papers/pldi2011/sigplanconf-template.tex

The \textit{lastChange} algorithm is based on program re-execution. \textit{Reproduction point} is the execution point in which first \textit{lastChange} is calld. Like the introductory example, it can be specified by a [conditional] breakpoint. \textit{lastChange} can be called on two different types of values: An object property or a variable value. In JavaScript, every available variable in a frame comes from one of the scopes in the current scope chain. There are five different scopes: global, local, with, catch, closure. We explain each case separately.

@@

\subsection{\textit{lastChange} on variable} 
Once developer asks for the last change of variable \texttt{foo} at a reproduction point, debugger first determines the variable's scope as follows:  Consider that in JavaScript, available variables are not resricted to local varialbes, but all variables in outer scopes are also accessible. The outer scopes are regualr JavaScript objects or closure scopes. The first group are usually created by calling \texttt{with()} function. The second group are created once a function is called. Therefore, there are theree cases for the escope of a variable, the current scope, an outer scope regular object or an outer scope clousure scope.

If the variable belongs to an outer scope regular object, debugger treats the case like \textit{lastChange} on an object property. In the other two cases, debugger sets breakpoints on the line the variable is defined and all lines the variable is assigned a new variable (including inner-functions). For example in Figure ~\ref{fig:js-closure}, if the execution is paused at line 24 and the last change of \texttt{var2} is requested by the developer, two breakpoints on lines 22 and 23 will be set, but if the execution is paused at line 19, four breakpoints on lines 11, 12, 16, and 18.

>>>>

The \textit{lastChange} algorithm is based on program re-execution. \textit{Reproduction point} is the execution point in which first \textit{lastChange} is calld. Like the introductory example, it can be specified by a [conditional] breakpoint. \textit{lastChange} can be called on two different types of values: An object property or a variable value. In JavaScript, every available variable in a frame comes from one of the scopes in the current scope chain. There are five different scope types: global, local, with, catch, closure. We explain each case separately.

@@

\subsection{\textit{lastChange} on variable} 
Once developer asks for the last change of variable \texttt{foo} at a reproduction point, debugger first determines the variable's scope as follows: it iterates over the scopes in the scope chain and the first scope which has a variable with the same name is the variable's scope. Consider that in JavaScript, available variables are not resricted to local varialbes, but all variables in outer scopes are also accessible. Among five scope types, global scopes and with scopes-scopes which are created by calling \texttt{with()} function-are regular JavaScript objects. Debugger treats the case where variable's scope is global or with, like \textit{lastChange} on an object property.

A closure scope is created once a function is called. In this case, debugger sets breakpoints on the line the variable is defined and all lines the variable is assigned a new variable (including inner-functions). For example in Figure ~\ref{fig:js-closure}, if the execution is paused at line 24 and the last change of \texttt{var2} is requested by the developer, two breakpoints on lines 22 and 23 will be set, but if the execution is paused at line 19, four breakpoints on lines 11, 12, 16, and 18.
